---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

## Create Daily Series from Google Trends

<!-- badges: start -->
[![Travis build status](https://travis-ci.com/trendecon/trendecon.svg?branch=master)](https://travis-ci.com/trendecon/trendecon)
<!-- badges: end -->

This package contains R code to construct long daily time series from Google Trends. Robustness of the data is achieved by querying Google mulitple times. The queries are sampled at daily, weekly and monthy frequencies and then harmonized such that the long term trend is preserved.

The website [www.trendecon.org](https://www.trendecon.org) applies the package and provides a set of indicators for Switzerland and is updated daily. During the Covid-19 pandemic, such high-frequency indicators have been in high demand. The economic and social situation has changed very rapidly and most economic statistics could not provide timely information since they are collected on a much lower frequency and published with a lag. We use Google search trends to create meaningful indicators that don't suffer from this problem. In particular, we extract daily search data on keywords reflecting consumers' perception of the economic situation.

The project was inititated during the [#versusvirus](https://www.versusvirus.ch) and got [funding](https://www.versusvirus.ch/funding) from the hackathon.

## Install

You can install the trendecon package from GitHub.


```r
# install.packages("remotes")
remotes::install_github("trendecon/trendecon")
```

## Usage


To download a series from Google Trends:

```{r}
library(trendecon)
x <- ts_gtrends("cinema", geo = "CH")
tsbox::ts_plot(x)
```

## Documentation

The [introductory vignette](https://trendecon.github.io/trendecon/articles/intro.html) describes the basic use of the package.

To create and update long daily series from Google Trends, see the [vignette on daily series](https://trendecon.github.io/trendecon/articles/daily-series.html).



## TODO


Main source for inormation: http://r-pkgs.had.co.nz

### Documentation


- [x] DESCRIPTION: authors, pkg summary
- [x] Introductiory vignette (`vignettes/intro.Rmd`) (http://r-pkgs.had.co.nz/vignettes.html)
- [x] Minimal section on getting started as `README.md`
- [x] pkgdown website (optional) https://pkgdown.r-lib.org
- [ ] Roxigen header to exported functions (http://r-pkgs.had.co.nz/man.html)
- [ ] Vignette: How to perform daily updates (see section below)




### Clean Up

- [ ] Turn scripts in `inst/script` into functions. Instead of `inst/script/clothing.R`, we want to have something like `R/proc_index_clothing.R` (the later is currently just an example).
- [ ] Define (and document) the use of system paths. I think the only place where they appear is now in `path_trendecon`. Perhaps use system variables.


### Tests

- [x] a very few tests of the basic functions (optional)
- [ ] R CMD check --as-cran (optional)




