---
title: "Creating long daily series"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Creating long daily series}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(trendecon)
```


## Intro

Google search results are available on a daily, weekly or monthly frequency. As with individual samples, querying Google at a different frequency will lead to substantially different results.

Our goal is to produce long daily time series, ideally from 2006. This is mostly because we want to use the financial crisis of 2008 and 2009 as a benchmark for the Covid-19 crisis. However, Google does not provide daily or weekly data for such a long time period. We circumvent the problem by applying a moving window of daily and weekly queries over the whole time period.

Since the daily, weekly and monthly series are still very different, we want to combine them into a single daily series.

Our next steps are based on the following assumptions:

- Monthly data catches the long term trend in search activity in the most accurate way.

- Weekly data is best to analyze the searches over the medium term, i.e., over a few months.

- Daily data is best to analyze short term behavior over a few days and weeks.

With this in mind, we apply the following methodology. In a first step, we "bend" the daily series to the weekly values, by applying a variant of the Chow-Lin (1971) method. This preserves the movement of the daily series and ensures that weekly averages are identical to the original weekly series.



## Setting the Data Path

```r
my_data_dir <- tempdir()
options(path_trendecon = my_data_dir)
```

- `proc_` functions will write and read to this directory.


## Initial Download

To include a new series, each keyword must be initiated. Careful, this causes a lot of queries to Google.


```r

proc_keyword_init("Rezession", "DE")
```



## Daily Update

Once all the keywords are initiated, the script updates the series and produces the indicator. The last line copies the data to the data repository.


```r
proc_keyword_latest()

```


## Further Steps

- Bending

- Seasonal Adjustment

- Index creation


## Reading and Writing

`read_keyword`
`write_keyword`


## Updating trendecon indicators (perhaps)

To source all scripts from trendecon, use:

```r
# remotes::install_local()   # build the package, only do once
trendecon::proc_all()
```







