---
title: "intro"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(trendecon)
```


Google Trends is an online search tool from Google that allows you to analyse the relative populatity of search queries. See https://trends.google.com/ for the official online interface. The tool allows to specify the time horizon and to define the location. Thereby, the popularity of a search term can be analysed over time, across countries and relative to other search terms.

The R package trendecon allows to produce long daily time series of search queries. With the main function of the package, `ts_gtrends()` Google Trends data is downloaded for one or multiple keywords or Google product categories. It wraps around the package gtrendsR but modifies the function [gtrendsR::gtrends()] by a) vectorizing it, b) converting the result to a tsboxable tibble and c) retrying if no result is returned.


## Keyword search

Suppose we are interested in the demand for cultural events in Switzerland. First think of what people would google if they want to go to a cultural event. For instance, they might google "cinema", "oper", "kino" and "theater". The following command downloads the Google Trends data for these search terms.


```{r}
gt_data <- ts_gtrends(keyword = c("cinema", "oper", "kino", "theater"),
                      geo = "CH",
                      time = "today+5-y")
```

Specify with the paramter `geo` the geographic location. Default is Switzerland ("CH"). With `geo=""` the global search volume is used. Not only countries but also regions within a country are possible. See `data("countries")` from the gtrendsR package for a list of available regions and their code.

With the parameter `time` the time span of the query can be specified. "today+5-y" downloads for the time span for the last five years (default). The frequency of the data depends on the entered time span. A time span of up to three months will yield daily data. Up to five years allows for a weekly frequency. And for a time span of more than five years, the data is monthly. `time = "all"` uses the maximum time span which starts in January 2004.

You can plot the time series with `ts_plot` from the `tsbox` package.

```{r}
ts_plot(gt_data)
```


To retrieve the common signal of the four time series, you can for instance draw the principal component.

```{r}
ts_plot(pc1 = filter(ts_prcomp(gt_data), id == "PC1"))
```




## Google product categories search

Alternatively to a search term also predefined Goolge product categories can be used. See for instance https://github.com/pat310/google-trends-api/wiki/Google-Trends-Categories for a hierarchically structered list of the Google product categories or get the categories with `data("categories")` from the gtrendsR package. Every search query in the Google search engine is assigned to one or multiple Google product categories. Therefore, the search volume of a category is an aggregate of multiple search terms. There is for instance the category "Events & Listings" with id 569.

```{r}
gt_data_cat <- ts_gtrends(category = "569",
                          geo = "CH",
                          time = "today+5-y")

ts_plot(gt_data_cat)
```




## Tips when using Google trends

* Check https://support.google.com/trends/answer/4365533?hl=en for FAQ about Google Trends data.
* On the use of punctuation: https://support.google.com/trends/answer/4359582?hl=en&ref_topic=4365530.
* The data is sampled from the Google Trends data base and cached for one day. Therefore, the same query may yield different search volumens on different days.

